О множествах точек на плоскости с целочисленными расстояниями

### 2019-05-30 pps-linear-bound/pps-linear-lower-bound.tex
Use shorter notaton for lengths of line segments

\begin{lemma}
	\label{lem:2k-1_segments}
	Let $M \in \mathfrak{M}(2,n)$ for some $n$ and let $m$ be a straight line.
	Then for every $k\in\mathbb{N}$ there are at most $2k-1$ segments $\Delta_i \subset m$,
	such that the length of $\Delta_i$ is exactly $k$.
\end{lemma}
\begin{proof}
	Consider a point $N\in M \setminus m$.
	Then for each $\Delta_i$ there is a $\rho(n_i,\Delta_i)$-curve containing $N$.
	Due to Observation~\ref{obs:rho_curves}, all $n_i$ are distinct;
	otherwise $\rho(n_i,\Delta_i)$-curve and $\rho(n_i,\Delta_j)$-curve, $j\neq i$, do not intersect.
	There can be only $2k-1$ different values for $n_i$,
	so there are at most $2k-1$ distinct segments $\Delta_i$.
\end{proof}

@@

\begin{lemma}
	Let $\Delta$ be a straight line segment of length $l$, $M \in \mathfrak{M}(2,n)$ for some $n$.
	Let $\#(\Delta \cap M) = n^2 + 1$.
	Then $l \geq \frac{2}{3}n^3+\frac{1}{2}n^2-\frac{1}{6}n$
	.
\end{lemma}

@@

\begin{lemma}
	Let $\Delta$ be a straight line segment of length $l$, $M \in \mathfrak{M}(2,n)$ for some $n>122$.
	Let $\#(\Delta \cap M) = k > 10000$.
	Then $l\geq \gamma_1 k^{3/2}$,
	TODO: why 10 000 ???
	where

@@

\begin{observation}
	\label{obs:estimate_points_on_straight_line}
	Let $\Delta$ be a straight line segment of length $l$, $M \in \mathfrak{M}(2,n)$ for some $n>21491$.
	Let $\#(\Delta \cap M) = k > 10000$.
	Then $k \leq \gamma_2 b + 6$,
	where

>>>>

\begin{lemma}
	\label{lem:2k-1_segments}
	Let $M \in \mathfrak{M}(2,n)$ for some $n$ and let $m$ be a straight line.
	Then for every $k\in\mathbb{N}$ there are at most $2k-1$ segments $\Delta_i \subset m$,
	such that $|\Delta_i| = k$.
\end{lemma}
\begin{proof}
	Consider a point $N\in M \setminus m$.
	Then for each $\Delta_i$ there is a $\rho(n_i,\Delta_i)$-curve containing $N$.
	Due to Observation~\ref{obs:rho_curves}, all $n_i$ are distinct;
	otherwise $\rho(n_i,\Delta_i)$-curve and $\rho(n_i,\Delta_j)$-curve, $j\neq i$, do not intersect.
	There can be only $2k-1$ different values for $n_i$,
	so there are at most $2k-1$ distinct segments $\Delta_i$.
\end{proof}

@@

\begin{lemma}
	Let $\Delta$ be a straight line segment, $|\Delta|=l$ and $M \in \mathfrak{M}(2,n)$ for some $n$.
	Let $\#(\Delta \cap M) = n^2 + 1$.
	Then $l \geq \frac{2}{3}n^3+\frac{1}{2}n^2-\frac{1}{6}n$
	.
\end{lemma}

@@

\begin{lemma}
	Let $\Delta$ be a straight line segment, $|\Delta| = l$ and $M \in \mathfrak{M}(2,n)$ for some $n>122$.
	Let $\#(\Delta \cap M) = k > 10000$.
	Then $l\geq \gamma_1 k^{3/2}$,
	TODO: why 10 000 ???
	where

@@

\begin{observation}
	\label{obs:estimate_points_on_straight_line}
	Let $\Delta$ be a straight line segment, $|\Delta| = l$ and $M \in \mathfrak{M}(2,n)$ for some $n>21491$.
	Let $\#(\Delta \cap M) = k > 10000$.
	Then $k \leq \gamma_2 b + 6$,
	where
